### 2024-05-10 README.Rmd
Run man, run while you can

friction_surface <- get_friction_surface(
    surface = "motor2020",
    extent = matrix(
      data = c("111", "0", "112", 1),
      nrow = 2,
      ncol = 2,
      dimnames = list(
        c("x", "y"),
        c("min", "max")
      )
    )
  )

plot(friction_surface)
```

```{r}
from_here <- tibble::tibble(
  x = c(111.2, 111.9),
  y = c(0.2, 0.35)
)

travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here
)

plot(travel_time)
points(from_here, pch = 19, add = TRUE)
```

>>>>

friction_surface <- get_friction_surface(
    surface = "motor2020",
    extent = matrix(
      data = c("111", "0", "112", 1),
      nrow = 2,
      ncol = 2,
      dimnames = list(
        c("x", "y"),
        c("min", "max")
      )
    )
  )
friction_surface
```

```{r}
plot(friction_surface)
```

```{r}
from_here <- tibble::tibble(
  x = c(111.2, 111.9),
  y = c(0.2, 0.35)
)
from_here
```

```{r}
travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here
)
travel_time
```

```{r}
plot(travel_time)
points(from_here, pch = 19, add = TRUE)
```
